DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-02-01 paper/evaluation.tex
cache partition section as a separate file.
for now it is not included.

In this section, we experimentally analyze various real-time aspects
of the DeepPicar. This includes
(1) measurement based worst-case execution time (WCET) analysis of
deep learning inferencing,
(2) the effect of using multiple cores in accelerating inferencing,
(3) the effect of co-scheduling multiple deep neural network models,
(4) the effect of co-scheduling memory bandwidth intensive co-runners,
and
(5) the effect of partitioning the shared L2 cache.

>>>>

In this section, we experimentally analyze various real-time aspects
of the DeepPicar. This includes
(1) measurement based worst-case execution time (WCET) analysis of
deep learning inferencing,
(2) the effect of using multiple cores in accelerating inferencing,
(3) the effect of co-scheduling multiple deep neural network models,
and 
(4) the effect of co-scheduling memory bandwidth intensive co-runners.
%% and
%% (5) the effect of partitioning the shared L2 cache.
